Exploring and Reverse Engineering the Motives Behind API Modifications

### 2015-03-27 rmtw/a6/latex8.tex
Added some bibs n stuff
added evolution section

\subsubsection{Software Evolution}
The concept of software evolution has existed since the 1960s, often being interchangeable with software maintenance. Well known studies from this era established the need for

>>>>

\subsubsection{Software Evolution}

Software evolution can be described as being the application of software maintenance activities and processes, resulting in a new, \textit{evolved} version of the software.

The concept of software maintenance has existed since the 1960s. Well known studies from this era established the importance of software maintenance \cite{canning1972maintenance}\cite{lientz1980software}. One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software. These categories were refined in a further study, which saw the count of categories increase from four to twelve \cite{chapin2001types}; enhancive,corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training.

Each category describes an intent behind changes to software, focusing around one of 3 particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}. This study also helped to further the distinction between software maintenance and software evolution. The study suggested that software maintenance is a part of software evolution and that the two are not interchangeable \cite{chapin2001types}.
